\documentclass[10pt]{exam}
%\printanswers
\usepackage{fullpage}

\setlength{\parindent}{0pt}
\setlength{\parskip}{.25cm}

\usepackage{graphicx}

\usepackage{xcolor}

\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\usepackage{hyperref}
\hypersetup{
  letterpaper,
  colorlinks,
  linkcolor=red,
  citecolor=darkgreen,
  menucolor=darkred,
  urlcolor=blue,
  pdfpagemode=none,
  pdftitle={Introduction To Git},
  pdfauthor={Christopher M. Bourke},
  pdfcreator={$ $Id: cv-us.tex,v 1.28 2009/01/01 00:00:00 cbourke Exp $ $},
  pdfsubject={PhD Thesis},
  pdfkeywords={}
}

\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45}
\definecolor{MyDarkRed}{rgb}{0.45,0.08,0}
\definecolor{MyDarkGreen}{rgb}{0.08,0.45,0.08}

\definecolor{mintedBackground}{rgb}{0.95,0.95,0.95}
\definecolor{mintedInlineBackground}{rgb}{.90,.90,1}

%\usepackage{newfloat}
\usepackage[newfloat=true]{minted}
\setminted{mathescape,
               linenos,
               autogobble,
               frame=none,
               framesep=2mm,
               framerule=0.4pt,
               %label=foo,
               xleftmargin=2em,
               xrightmargin=0em,
               startinline=true,  %PHP only, allow it to omit the PHP Tags *** with this option, variables using dollar sign in comments are treated as latex math
               numbersep=10pt, %gap between line numbers and start of line
               style=default, %syntax highlighting style, default is "default"
               			    %gallery: http://help.farbox.com/pygments.html
			    	    %list available: pygmentize -L styles
               bgcolor=mintedBackground} %prevents breaking across pages
               
\setmintedinline{bgcolor={mintedBackground}}
\setminted[text]{bgcolor={mintedBackground},linenos=false,autogobble,xleftmargin=1em}
%\setminted[php]{bgcolor=mintedBackgroundPHP} %startinline=True}
\SetupFloatingEnvironment{listing}{name=Code Sample}
\SetupFloatingEnvironment{listing}{listname=List of Code Samples}

\begin{document}

\section*{CSCE 155 - Lab 15 - Databases - Worksheet}

Names: \underline{\hspace{10cm}}

\begin{questions}

\question Look over the code provided in the \mintinline{text}{games.h} 
and \mintinline{text}{games.c} header and source file and answer the following.
\begin{parts}
  \part Which function should be used to add a platform to the database 
  and what are its parameters?
  \begin{solution}[2cm]
  \end{solution}

  \part What type of SQL query is used to add records to the database 
  (hint: look at the \mintinline{c}{addPlatform}, \mintinline{c}{addVideoGame},
  \mintinline{c}{addPublisher} functions)?
  \begin{solution}[2cm]
  \end{solution}

  \part What type of SQL query is used to retrieve records from the 
  database (hint: look at the \mintinline{c}{getGame}, 
  \mintinline{c}{getPlatform}, etc. functions).
  \begin{solution}[2cm]
  \end{solution}
  
\end{parts}

\question Data Integrity

\begin{parts}

  \part What error messages did you get and why?
  \begin{solution}[2cm]
  \end{solution}
  
  \part A bad database design may not have properly defined the foreign 
  keys between the game and publisher tables, instead allowing the bad 
  game data that we attempted to insert into the database.  What 
  consequences could this have for a larger application?
  \begin{solution}[2cm]
  \end{solution}

  \part Consider the following: two programs or users use our API to add 
  two different games to the database, both PlayStation 3 games.  
  However, the first user inserts the platform as ``PS3'' and the second 
  inserts it as ``PlayStation III''.  Would this result in an error?  
  What would the consequences of this be for a larger application?
  \begin{solution}[2cm]
  \end{solution}

  \part Say that we wanted to remove a publisher from the database.  
  What would we need to do before we could remove the record?
  \begin{solution}[2cm]
  \end{solution}

\end{parts}

\question Demonstrate your working programs to a lab instructor.  

\end{questions}
  
Lab Instructor Signature\underline{\hspace{7.5cm}}

\end{document}
